### 2018-10-30 main_analyses.Rmd
journal

Libraries
```{r}
  library(broom)
  library(purrr)
  library(readr)
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(stringr)
  library(feather)
  library(lme4)
  library(boot)
  library(langcog)
  library(ggthemes)
  library(nlme)
  library(rwebppl)
  library(jsonlite)
  library(Hmisc)
  library(poweRlaw)
  library(HDInterval)
```

@@

@@

#I should here define the set of words that will be used in the network construction
#Here I chose to use the full data for the phono netwotk and filter later for the unilemmas only, thus the utility will be more precise for the resulting subset

@@

  lemma_list<- growth_meas_lang %>%
      trim_all_unilemma() %>%
      filter(age==first_age) %>%
      select(item, uni_lemma)

@@

#Save 
#feather::write_feather(sem_red, "saved_data/sem_red.feather")
#sem_red <- feather::read_feather("saved_data/sem_red.feather")

@@

#feather::write_feather(phono_red, "saved_data/phono_red.feather")
#phono_red <- feather::read_feather("saved_data/phono_red.feather")

@@

#Word frequency: we use frequency values derived from Childes (from Mika e al. 2016)

load("saved_data/uni_joined.RData")

@@

```{r}
#Sem_deg is defined over unilemmas,  phono_deg is defined over definitions, and AoA is defined over items 
#For a given defintion we can have more than one item (polysemy), for one unilemma we can have more than one definiton (if the semantic distinction is not very important), or we might have 0 unilemma (if the meaning of the defintion is not part of the main cross-lingusitc lemmas)
#The following analyses predict try to predict the items' AoA. I keep duplicated values of the predictors for different items (when they have the same defintions and/or unilemma) since I consider that this is the actual (albeit braod) information brough by the precitors

@@

### Small world properties

Use igraph to derive small world properties

For each netwrok, compute:
-Clustering coefficient 
-Shortest path length 
what we want: Compared to an equivalent random network, we want a balance between local processing (high clustering coefficient) and global integration (small short path length)

@@

#Filtering 
data_growth_pred <- data_growth_net %>%
  filter(!is.na(uni_lemma)) %>% #use only words with english translation 
  filter(!is.na(PAC_assoc)) %>% # keep unilemma whcih intersect with free association data
  filter(!is.na(PAC_phono_t2)) # In case a word is not trnascribed phonologically (there should not be any)

>>>>

Libraries
```{r}
  library(broom)
  library(purrr)
  library(readr)
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(stringr)
  library(feather)
  library(lme4)
  library(boot)
  library(langcog)
  library(ggthemes)
  library(nlme)
  library(rwebppl)
  library(jsonlite)
  library(Hmisc)
  library(poweRlaw)
  library(HDInterval)
  library(kableExtra)
```

@@

Here compute the statistics 
language, measure, number of nouns, age limits, and number  
```{r}

mysummary <- data_all %>%
  group_by(language, measure) %>%
  summarise(min_age = min(age),
            max_age = max(age),
            nouns = n_distinct(item)) %>%
  mutate(age_range = paste(min_age, max_age, sep = "-")) %>%
  select(-min_age, -max_age)  %>%
  group_by(language, measure) %>%
  nest() %>%
  spread(measure, data) %>%
  unnest(.sep = "_") %>%
  select(language, un = understands_nouns, ua=understands_age_range,
                   pn = produces_nouns, pa=produces_age_range)

feather::write_feather(mysummary, "saved_data/stats_new.feather")

kable(mysummary, format = "latex", escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for data from Wordbank.",
      col.names = c("Language",  "Nouns", "Ages", "Nouns", "Ages")) %>%
  add_header_above(c("", "Comprehension" = 2, "Production" = 2)) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

@@

#Here I chose to use the full data for the phono netwotk and filter later for the unilemmas only when doing what? the combined regression?, thus the utility will be more precise for the resulting subset

@@

  lemma_list<- growth_meas_lang %>%
      trim_all_unilemma() %>% #For semantic netowtks only the unilmma
      filter(age==first_age) %>%
      select(item, uni_lemma)

@@

#Save 
#feather::write_feather(sem_red, "saved_data/sem_red.feather")
sem_red <- feather::read_feather("saved_data/sem_red.feather")

@@

#feather::write_feather(phono_red, "saved_data/phono_red.feather")
phono_red <- feather::read_feather("saved_data/phono_red.feather")

@@

#Word frequency: we use frequency values derived from Cross-lingusitic corpora in CHILDES (from Mika e al. 2016) 
load("saved_data/uni_joined.RData")

@@

#Sem_deg is defined over unilemmas,  phono_deg is defined over definitions, and AoA is defined over items 
#For a given defintion we can have more than one item (polysemy), for one unilemma we can have more than one definiton (if the semantic distinction is not very important), or we might have 0 unilemma (if the meaning of the defintion is not part of the main cross-lingusitc lemmas)
#The following analyses predict the items' AoA. I keep duplicated values of the predictors for different items (when they have the same defintions and/or unilemma) since I consider that this is the actual (albeit braod) information brough by the precitors

@@

@@

#Filtering 
data_growth_pred <- data_growth_net %>%
  filter(!is.na(uni_lemma)) %>% #use only words with english translation 
  filter(!is.na(PAC_assoc)) %>% # keep unilemma which intersect with free association data
  filter(!is.na(PAC_phono_t2)) # In case a word is not transcribed phonologically (there should not be any)
